---
title: "BeautifySJ Requests Demographic Descriptors Analysis"
author: "Michael Spencer, Barbara Cardona, Guillermo Camarillo, Jorge Nam Song"
date: "2/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
## Setup

### Libraries
if (!require(tidycensus)) install.packages("tidycensus")
library(tidycensus)

if (!require(sf)) install.packages("sf")
library(sf)

if (!require(lubridate)) install.packages("lubridate")
library(lubridate)

if (!require(tidyverse)) install.packages("tidyverse")
library(tidyverse)

### Parameters
write_my_files <- "no" # Change this if you would like fresh data files downloaded
keep_geometry <- "no" # Change this if you plan on mapping the data here in R

vars_of_interest <- c(
	"linguistic_isolation_(percent_households)",
	"bg_ed_percent_college_educated",
	"bg_med_age",
	"bg_percent_prop_households_owner_occ",
	"bg_percent_prop_households_renter_occ",
	"bg_pop_percent_white",
	"bg_pop_percent_hispanic",
	"bg_pop_percent_asian",
	"bg_med_income",
	"cellular_data_subscription_(percent_of_pop)",
	"broadband_subscription_(percent_of_pop)",
	"bg_med_home_value"
)


### Source Data
source("../scripts/support/support_functions.R")
source("../scripts/data/final_clean.R")
```

## Summary Tables & Charts
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	count(incident_source, sort = TRUE) %>% 
	mutate(percent_of_total = (n/sum(n)) %>% round(digits = 4))

data_requests %>% 
	count(service_requested, sort = TRUE) %>% 
	mutate(percent_of_total = (n/sum(n)) %>% round(digits = 4))

data_requests %>% 
	group_by(incident_source, service_requested) %>% 
	summarise(n = n()) %>% 
	mutate(percent_of_source = (n/sum(n)) %>% round(digits = 4)) %>% 
	arrange(incident_source, desc(percent_of_source)) %>% 
	ungroup() %>% 
	mutate(percent_of_total = (n/sum(n)) %>% round(digits = 4))
 
data_requests %>% 
	count(request_creation_weekday, sort = TRUE) %>% 
	mutate(percent_of_total = (n/sum(n)) %>% round(digits = 4))

data_requests %>% 
	count(san_jose_council_district, sort = TRUE) %>% 
	mutate(percent_of_total = (n/sum(n)) %>% round(digits = 4))

data_requests %>% 
	count(census_block_id, sort = TRUE) %>% 
	mutate(percent_of_total = (n/sum(n)) %>% round(digits = 4)) %>% 
	top_n(10, wt = percent_of_total)
```

```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	count(census_block_id, sort = TRUE) %>% 
	mutate(percent_of_total = (n/sum(n)) %>% round(digits = 4)) %>% 
	ggplot(aes(x = percent_of_total)) +
	geom_histogram(bins = 30, color = "black", fill = "white") +
	scale_x_continuous(labels = scales::percent_format()) +
	theme_minimal() +
	labs(
		title = "Distribution of Requests Across Census Block Groups",
		subtitle = "The distribution is right skewed, indicating that a handful of block groups\nrecieve a larger amount of requests than most others.",
		x = "Percent of Total Requests",
		y = "Count",
		caption = "Source: City of San Jose"
	)
```

\newpage
## Demographics of Requesting Census Block Groups
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% distinct(census_block_id) %>% 
	left_join(data_descriptive, by = "census_block_id") %>% 
	summarize_at(
		vars_of_interest, 
		list(
			xthirtieth_percentile = ~quantile(., .3, na.rm = TRUE),
			xmedian = median,
			xseventieth_percentile = ~quantile(., .7, na.rm = TRUE)
		), 
		na.rm = TRUE
	) %>%
	gather(key = "var", value = "val") %>% 
	mutate(val = val %>% format(scientific = FALSE, digits = 3)) %>%
	separate(var, into = c("var", "percentile"), sep = "_x") %>% 
	spread(key = percentile, value = val) %>% 
	select(var, thirtieth_percentile, median, seventieth_percentile) %>% 
	arrange(desc(var)) %>% 
	knitr::kable()
```


\newpage
## Demographic Descriptors By Channel

\newpage
### All Requests

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>%
	knitr::kable()

data_requests %>% 
	gather_data() %>% 
	find_demographic_descriptors_var() %>%
	knitr::kable()
```

\newpage
#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()

data_requests %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors_var() %>% 
	knitr::kable()
```

\newpage
#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()

data_requests %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors_var() %>% 
	knitr::kable()
```

\newpage
#### Agent Desktop
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	gather_data(request_source = "Agent desktop") %>% 
	find_demographic_descriptors() %>%
	knitr::kable()

data_requests %>% 
	gather_data(request_source = "Agent desktop") %>% 
	find_demographic_descriptors_var() %>%
	knitr::kable()
```

\newpage
## Demographic Descriptors By District

\newpage
### District 1

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 1) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 1) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 1) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 2

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 2) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 2) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 2) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 3

#### All MySanJose Platforms
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 3) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 3) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 3) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 4

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 4) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 4) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 4) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 5

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 5) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 5) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 5) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 6

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 6) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 6) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 6) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 7

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 7) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 7) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 7) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 8

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 8) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 8) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 8) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 9

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 9) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 9) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 9) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### District 10

#### All MySanJose Platforms

```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 10) %>% 
	gather_data() %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 10) %>% 
	gather_data(request_source = "Mobile") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE, out.height='50%', out.width='50%'}
data_requests %>% 
	filter(san_jose_council_district == 10) %>% 
	gather_data(request_source = "Web") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
## Demographic Descriptors By Channel and Request Type

\newpage
### Abandoned Vehicle

#### All MySanJose Platforms
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_type = "Abandoned Vehicle") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Mobile", request_type = "Abandoned Vehicle") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Web", request_type = "Abandoned Vehicle") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### Illegal Dumping

#### All MySanJose Platforms
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_type = "Illegal Dumping") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Mobile", request_type = "Illegal Dumping") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Web", request_type = "Illegal Dumping") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### General Requests

#### All MySanJose Platforms
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_type = "General Request") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Mobile", request_type = "General Request") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Web", request_type = "General Request") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### Graffiti

#### All MySanJose Platforms
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_type = "Graffiti") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Mobile", request_type = "Graffiti") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Web", request_type = "Graffiti") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### Streetlight Outage

#### All MySanJose Platforms
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_type = "Streetlight Outage") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Mobile", request_type = "Streetlight Outage") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Web", request_type = "Streetlight Outage") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

\newpage
### Pothole

#### All MySanJose Platforms
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_type = "Pothole") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Mobile App
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Mobile", request_type = "Pothole") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```

#### MySanJose Web Platform
```{r, echo=FALSE, warning=FALSE}
data_requests %>% 
	gather_data(request_source = "Web", request_type = "Pothole") %>% 
	find_demographic_descriptors() %>% 
	knitr::kable()
```


## Duplicates Analysis
```{r}
data_requests %>% 
	mutate(
		date = date(date_created) %>% as.character(),
		latitude = latitude %>% round(digits = 3),
		longitude = longitude %>% round(digits = 3)
	) %>% 
	count(request_creation_year, request_creation_month, service_requested, latitude, longitude, census_block_id, sort = TRUE) %>% 
	mutate(latitude = as.character(latitude), longitude = as.character(longitude))

data_requests %>% 
	mutate(
		date = date(date_created) %>% as.character(),
		latitude = as.character(latitude), 
		longitude = as.character(longitude)
	) %>% 
	filter(
		date == "2019-02-27",
		service_requested == "Abandoned Vehicle",
		latitude == "37.3074934",
		longitude == "-121.8783636",
		census_block_id == "060855031211"
	)
```

```{r}
data_requests %>% 
	mutate(
		date = date(date_created) %>% as.character(),
		latitude = latitude %>% round(digits = 3),
		longitude = longitude %>% round(digits = 3)
	) %>%
	distinct(service_requested, latitude, longitude, request_creation_year,request_creation_month, census_block_id)
```

